
% \cvsection{Honors \& Awards}
% \begin{itemize}
%     \item Received accolades at Atos for Best Performance in team.
%     \item Received Best Debut Award at Atos.
%     \item Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.
%     \item Awarded with Narotam Sekhsaria Foundation Scholarship
% \end{itemize}
% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

%\cvtag{Hard-working (18/24)} 
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}


%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}

\cvsection{SKILLS}

\cvskill{Python, JavaScript}{4}
\cvskill{Flask, Django, unittest}{3}
\cvskill{jQuery, jQuery UI, ReactJS}{4}
%\divider

\cvskill{PostgreSQL, MongoDB}{3}
\cvskill{AWS, Unix, Git }{3}
% \divider
%\cvskill{German}{3}


\cvsection{Projects}

\cvproject{Send Later App}
\begin{itemize}
\item An add-on for Flock (a Slack like messaging platform) which allows user to send messages anytime in future.
\item Uses an Express JS (Node JS) based back-end server deployed on cloud with PostgreSQL database for persistence.

\end{itemize}
\smallskip
\cvproject{Data Cold Storage}
\begin{itemize}
\item Web platform for Archival storage of rarely used data made using Django \& React.
\item Leverages AWS's cheap S3 Glacial storage instead of regular option.
\item Load balancing using AWS's simple queue service.
\end{itemize}
\smallskip
\cvproject{URL Shorter Service}
\begin{itemize}
\item Developed a Django based web platform to shorten long URL's which look good when shortened.
\item Used python unittest for test driven development
\end{itemize}
\smallskip

\cvproject{Ad blocker}
\begin{itemize}
\item An Ad-blocker for Chrome \& Firefox to get rid of annoying ads on each website you visit.
\item Shows analytical dashboard of historical blocking stats. 
\end{itemize}

\cvproject{Billing System : ERP}
\begin{itemize}
\item A  billing  system  for  my  friend's  Bottle  distribution  company as a web-app built using Flask(Python), PostgreSQL, \& JQuery.
\end{itemize}



\cvsection{Extracurricular}
\smallskip
\begin{itemize}
\item Solving issues reported by users of tabulator.js (An open source JS library) on GitHub.
\smallskip
\item Participating in online coding competitions.
\smallskip
\end{itemize}

\cvproject{}